---
title: "Dark Chocolate Ratings"
author: "Paul Lazarescu"
date: "2022-10-16"
output:
  pdf_document: default
  html_document: default
---

# Business Objective
Our project manager is looking for which countries produce the highest-rated
bars of super dark chocolate (a high percentage of cocoa).
This data will help them create their next chocolate bar menu.


## Preview
First, we start by checking our working directory. A working directory simply means
the folder within which our files are stored. If the wd is incorrect or changes, roll
back to base ("~/"), then set to correct folder location.
Afterwards, we load the 'tidyverse' and 'rlang' packages for our analysis, as well as our dataset.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = '/Users/paull/OneDrive/Documents/My Data Sources')

#getwd()
#setwd("~/")
#getwd()
#setwd("/Users/paull/OneDrive/Documents")
#getwd()

install.packages("tinytex", repos = "http://cran.us.r-project.org")
library("tinytex")
install.packages("tidyverse", repos = "http://cran.us.r-project.org")
library("tidyverse")
install.packages("rlang", repos = "http://cran.us.r-project.org")
library("rlang")
install.packages("readr", repos = "http://cran.us.r-project.org")
library("readr")
#import dataset from working directory
#tinytex is for PDF functionality
```

We run a few pieces of code that show us the data we are working with.
```{r read, include=FALSE}
chocolate_df <-read_csv("flavors_of_cocoa.csv")
#str(chocolate_df) #raw summary
#glimpse(chocolate_df) #horizontal
```

```{r colnames}
colnames(chocolate_df)
```

```{r head}
head(chocolate_df) #vertical
```


Before we trim down the dataset. Let's see what the highest rating possible is, and let's see how many countries
we are working with.
```{r trim, echo=FALSE}
trimmed_flavors_df <- chocolate_df %>%
  select(Rating, `Cocoa
Percent`, `Company
Location`)
```

```{r max}
print(max(trimmed_flavors_df$Rating))
```

```{r distinct}
n_distinct(trimmed_flavors_df$`Company
Location`)
```
The highest rating attainable is a five, and the number of cocoa source locations is sixty.


## Preparation
In order to answer the business objective, we must filter for the data we are going to be using. We choose 3.5 because that represents a relatively high rating, and a cocoa percent of at-least 70%, as that is considered "dark" chocolate within our industry. For the purpose of ad-hoc analysis, this work perfectly.

```{r best}
best_trimmed_flavors_df <- trimmed_flavors_df %>%
  filter(Rating >= "3.5", `Cocoa
Percent` >= "70%")
view(best_trimmed_flavors_df)
```

```{r graph1, echo=FALSE, warning=FALSE}
graph1 <- ggplot(data = best_trimmed_flavors_df, aes(x=Rating)) +
  geom_bar(mapping = aes(x = Rating, fill = "Rating")) +
  geom_text(stat = 'count', aes(label=..count..), vjust=-0.25) +
  labs(title="Number of Ratings Received",
       caption=paste0("*Cocoa Percent over 70"),
       x="Rating",
       y="Count")
plot(graph1)
```

Above is a visualization that shows the distribution of ratings. What it shows us is that there are very few dark chocolates that receive perfect ratings, but there are quite a lot between 3.5 to 4.0. This gives us ample sample size to work with.
*Additional exploratory analysis also showed that the majority of ratings fall below 4.0, irrespective of cocoa percentage.*

```{r clean, include=FALSE}
install.packages("janitor", repos = "http://cran.us.r-project.org")
library("janitor")
#Janitor allows us clean up our dataset.
best_cleaned <- best_trimmed_flavors_df %>% 
  clean_names()
best_cleaned
#This is because the visualization tools in R limits what characters can be used in the ggplot2 graph code.
#Clean_names() reforms the column names so that they can be used in our code for visualization.
#Above, we see the dataset with our reformed column names.
#In order to visualize the data more effectively, we must rename our column names.
```


## Analysis

We want to see which countries produce the highest-rated dark chocolate. We have established a minimum cocoa percentage of 70%, a lowest rating of 3.5, and will be using a baseline (n) count of 20 ratings to give us an accurate sample size.

```{r rated}
highest_rated3 <- filter(summarise(group_by(best_cleaned, company_location), count=n(), mean(rating)), count >= 20)

```

```{r graph2, echo=FALSE}
names(highest_rated3)[names(highest_rated3) == "count"] <- "count_bars"
names(highest_rated3)[names(highest_rated3) == "mean(rating)"] <- "rating"
```
```{r graph3}
print(highest_rated3[order(highest_rated3$rating, decreasing = TRUE), ])
```
Our table, sorted by highest ratings.
Let's create a graph to visualize these findings.


```{r graph4, echo=FALSE}
highest_rated_location <- ggplot(highest_rated3, aes(x = company_location, y = rating)) + 
  geom_point(stat = "identity", size = 3.35) +
  theme(axis.text.x = element_text(angle = 25)) +
  labs(title="Locations with Highest-Rated Dark Chocolate",
       caption=paste0("*Minimum 20 ratings"),
       x="Company Location",
       y="Rating")
plot(highest_rated_location)
##highest_rated_location + labs(caption = c("*Cocoa Percent over 70", "*Minimum 20 ratings")) +
 ## theme(plot.caption = element_text(vjust = c(0, 0.37)))
##additional code not used during plotting
```

According to the graph, the location that provides us with the highest-rated bars of super dark chocolate is **Italy**. This analysis may be used as the basis for sourcing a larger quantity of our dark chocolate from the country of Italy.


## Conclusion
To surmise, our stakeholder was looking to find out which country produced the highest rated dark-chocolate. According to the findings, that country was: Italy, followed by France and then Australia.
We can use this information to source more of our inventory from the most economically-viable source.

Further analysis can be done by varying the levels of cocoa in the chocolate, joining a table containing shipping data
and costs, finding the top-producing companies in a given region, or looking at specific bean origin.
    